\LARGE \bf Multi-Arm Bandit Models for 2D Sample Based Grasp Planning with Uncertainty [v15 March 15, 2015 ]

### 2015-03-15 paper.tex
v15

\title{\LARGE \bf
Multi-Arm Bandit Models for 2D Grasp Planning with Uncertainty  [v11 March 13, 2015 ] }

@@

\begin{abstract}
For applications such as warehouse order fulfillment, robot grasps must be robust to uncertainty arising from sensing, shape, mechanics, and control.  One way to achieve this is to evaluate the performance of candidate grasps by sampling perturbations in shape, pose, and control, computing the probability of force closure for each candidate to identify the grasp with the highest expected quality.  This can be computationally demanding. To improve efficiency, we consider how Multi-Armed Bandit (MAB) models for optimizing sequential decisions can be applied in this context. We formulate robust grasp planning as a MAB problem and evaluate grasp planning convergence time using 100 object shapes randomly selected from from the Brown Vision 2D Lab Dataset with 1000 uniformly distributed candidate grasp angles. We consider the case where shape uncertainty is represented as a Gaussian process implicit surface (GPIS) and there is Gaussian uncertainty in pose, gripper approach angle, and coefficient of friction.  Non-MAB methods, uniform allocation and iterative pruning, converge slowly.  In contrast, the MAB methods we consider, Thompson Sampling and the Gittins Index, were more efficient in experiments, converging to within 3\% of the optimal grasp 10x faster than non-MAB methods.
\end{abstract}

@@

Consider a robot fulfilling orders in a warehouse, where it encounters new consumer products and must handle them quickly.
Planning grasps using analytic methods requires the contact locations and surface normals.
However, a robot may not be able to measure these quantities exactly due to sensor imprecision and missing data, which could result from occlusions, transparency, or highly reflective surfaces.

@@

    \caption{\todo{figure is only averaged over 40 shapes, rerunning the experiments (Shouldn't change earlier results on (TS, IP and UA ) once done)} Grasp quality over time for 4 sample-based planning methods compared with optimal grasp determined by brute force search over all candidate grasps (which required 10x  more time than any of these methods \cite{kehoe2012toward}).  Data is based on 100 objects randomly selected from from the Brown Vision 2D Lab Dataset \cite{brown} with 1000 uniformly distributed candidate grasp angles. Monte Carlo methods such as Uniform sampling and iterative pruning (eliminating candidates that perform poorly on initial samples) eventually converge to within 3$\%$ of the optimal, requiring approximately 40,000 and 20,000 iterations.  Two Multi-Arm Bandit methods perform significantly better, converging after only 4000 and 2000 iterations. }%
    \label{fig:grasp_quality}
\end{figure}

One common measure of quality is force closure, the ability to resist external forces and torques in arbitrary directions~\cite{li1988task}.To cope with uncertainty, recent work has explored computing the probability of  force closure given uncertainty in pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
One way to compute the probability of force closure is using Monte-Carl integration over sample perturbations in the uncertain quantities\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012toward}. However, performing Monte-Carlo integration for each candidate grasp in a set is computationally expensive.

We show that by using a Multi-Armed Bandit (MAB) model it is possible to allocate sampling effort to only grasps that seem promising \cite{barto1998reinforcement, lai1985asymptotically, robbins1985some}. In a standard MAB there are a set of possible options, or `arms'~\cite{barto1998reinforcement}, that each return a numeric reward from a stationary distribution. The goal in a MAB problem is to  select a sequence of options to maximize expected reward. We formulate the problem of ranking a set of candidate grasps according to a quality metric in the presence of uncertainty as a MAB problem. We then treat the MAB algorithm as an anytime algorithm that terminates once a user defined confidence level is met or at a given stopping time.

@@

We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem, against uniform allocation and an adaptive sampling method known as Iterative Pruning, which iteratively reduces the set of candidate grasps  based on sample mean~\cite{kehoe2012toward}. In the task of finding grasps with high probability of force closure.
We compare on the Brown Vision 2D Dataset, a dataset of 2D object silhouettes~\cite{brown, christopoulos2007handling}.
Our initial results in simulation show that the Gittins Index, a MAB algorithm, required $808\%$ fewer samples than Iterative Pruning to plan a grasp within $3\%$ of the estimated highest probability of force closure in the set of 1000 randomly selected grasps averaged over 100 objects.

@@

Some probabilistic grasp quality measures, such as probability of force closure, are computed using Monte-Carlo integration~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012toward}.
Monte-Carlo involves sampling from distributions on uncertainty quantities and averaging the quality over these samples to empirically estimate a probability distribution~\cite{caflisch1998monte}.
However, it can be computationally expensive to sample all proposed grasps to convergence.
To address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure called Iterative Pruning, which periodically discards a subset of the grasps that seem unlikely to be of high probability of force closure. However, the method pruned grasps using only the sample mean, which could discard good grasps.
We propose modeling the problem as a Multi-Armed Bandit, which selects the next grasp to sample based on past observations instead~\cite{barto1998reinforcement, lai1985asymptotically}.

\subsection{MAB Model}
\todo{Ken, you mentioned this section might seem condescending to the OR community. It be great if you can point out specifics here}
The MAB model, originally described by Robbins \cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision. Solutions to the MAB model have been used in applications for which evaluating all possible options is expensive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.

@@

At each time step the MAB algorithm incurs \textit{regret}, the difference between the expected reward of the best arm and that of the selected arm. Bandit algorithms minimize cumulative regret, the sum of regret over the entire sequence of arm choices.
Lai and Robbins showed that the cumulative regret of the optimal solution to the bandit problem is bounded by a logarithmic function of the number of arm pulls~\cite{lai1985asymptotically}.
They presented an algorithm called (Upper Confidence Bound) UCB that obtains this bound asymptotically~\cite{lai1985asymptotically}.
The algorithm maintains a confidence bound on the distribution of reward based on prior observations and pulls the arm with the highest upper confidence bound.
%Many variants of UCB have thus been proposed~\cite{cesa2006prediction}.

@@

\subsubsection{The Gittins Index Method} 
One MAB method is to treat the problem as a Markov Decision Process (MDP) and use Markov Decision theory.
Formally, a MDP is defined as a set of possible of states, a set of actions, a set of transition probabilities between states, a reward function, and a discount factor \cite{barto1998reinforcement}.
In the Beta-Bernoulli MAB case, the set of actions is the $K$ arms and the states are the Beta posterior on each arm, or the integer values of $\alpha_{k,t}$ and $\beta_{k,t}$.

@@

\subsubsection{Thompson Sampling}
Computation of the Gittins indices can increase exponentially in time as the discount factor approaches $1$. The problem with this is that the effective time horizon is a function of $\gamma$. Thus, if your actual horizon is longer than the effective horizon, the method has a policy of Follow the Leader, where it only pulls the current estimate of the best arm \cite{kelly1981multi}. Thompson sampling is an alternative to the GIttins Index method that isn't prone to such a problem. 
All arms are initialized with prior Beta distributions, which is normally Beta($\alpha_{k,0}=1$,  $\beta_{k,0} =1$) $\forall 1 \leq k \leq K$ to reflect a uniform prior on the parameter of the Bernoulli distribution, $p_{k,0}$.
Then for each arm draw $p_{k,t} \sim \mbox{Beta}(\alpha_{k,t},\beta_{k,t})$ and pull the arm with the highest $p_{k,t}$ drawn.
A reward is then observed, $R_{k,t}$ and the corresponding Beta distribution is updated. This is repeated until a stopping time is reached. The full algorithm is shown in Algorithm 2.

@@

\subsection{Candidate Grasp Model}
The grasp model is illustrated in Fig.~\ref{fig:grasp_model}. We formulate the MAB problem for 2-dimensional objects using parallel-jaw grippers. Similar to~\cite{mahler2015gp}, we parameterize a grasp using a {\it grasp axis}, the axis of approach for two jaws,  with jaws of width $w_j \in \mathbb{R}$ and a maximum width $w_g \in \mathbb{R}$. The two location of the jaws can be specified as $\mathbf{j}_1,\mathbf{j}_2 \in \mathbb{R}^2$, where $||\mathbf{j}_1 - \mathbf{j}_2|| \leq w_g$. We define a grasp plan consisting of the tuple $\Gamma = \lbrace \mathbf{j}_1, \mathbf{j}_2 \rbrace$.

%We chose of the line of action model because perturbations to a surface resulting from shape uncertainty lead to changesa in the location of contact with a surface, and the line of action allows us to compute these new locations.
\todo{Ken, the next section was crossed out in your notes, I'm still not clear on whats wrong with it. Can you elaborate more?}
Given a grasp plan and a object, we define the {\it contact points} as the spatial locations at which the jaws come into contact with the object when following along the grasp axis, $\bc_1, \bc_2 \in \mathbb{R}^2$.
We also refer to the unit outward pointing surface normals at the contact points as $\bn_1, \bn_2 \in \mathbb{R}^2$, the object center of mass as $\bz \in \mathbb{R}^2$ and the friction coefficient as $\mu \in \mathbb{R}$.
%Together these form the set of grasp parameters that allows us to evaluate the forces and torques that a given grasp can apply to an object \cite{ferrari1992}.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width = 6cm, height = 6cm]{figures/Graphical_Model.jpg}
\caption{A graphical model that illustrates the relationship between the different types of uncertainty in an object. As illustrated uncertainty in pose, motion and shape affect the contacts and surface normals that makes up the grasp. Friction coefficient is independent of this relationship. The box around contact and normals means they are repeated nodes, in this case we have $m=2$ corresponding to the two jaws in the gripper.  }
\vspace*{-10pt}
\label{fig:graphical_model}
\end{figure}

@@

Uncertainty in object shape results from sensor noise and missing sensor data, which can occur due to transparency, specularity, and occlusions~\cite{mahler2015gp}.
Following ~\cite{mahler2015gp}, we represent the distribution over possible surfaces given sensing noise using a Gaussian process implicit surface (GPIS).
A GPIS represents a distribution over signed distance functions (SDFs).
A SDF is a real-valued function over spatial locations $f: \mathbb{R}^2 \rightarrow \mathbb{R}$ that is greater than 0 outside the object, 0 on the surface and less than 0 inside the object.
A GPIS is a Gaussian distribution over SDF values at a fixed set of query points $\mX = \{\bx_1, ... \bx_n\}, \bx_i \in \mathbb{R}^2$, $f(\bx_i) \sim \mN(\mu_{f}(\bx_i),\Sigma_{f}(\bx_i))$, where $\mu_{f}(\cdot)$ and $\Sigma_{f}(\cdot)$ are the mean and covariance functions of the GPIS~\cite{rasmussen2006}.
See Mahler et al. for details on how to estimate a mean and covariance function and sample shapes from a GPIS~\cite{mahler2015gp}.
For convenience, in later sections we will refer to the GPIS parameters as $\theta = \lbrace \mu_{f}(\bx), \Sigma_{f}(\bx) \rbrace$.

@@

 \subsubsection{Approach Uncertainty}
In practice a robot may not be able to execute a desired grasp plan $\Gamma = \lbrace \bj_i,\bj_2\rbrace$ exactly due to errors in actuation or feedback measurements used for trajectory following~\cite{kehoe2012estimating}.
We model approach uncertainty as Gaussian uncertainty around the angle of approach and centroid of a straight line grasp plan $\Gamma$.
Formally, let $\hat{\by} = \frac{1}{2} (\bj_1 + \bj_2)$ denote the center of a planned grasp axis and $\hat{\psi}$ denote the angle that the planned axis $\bj_1 - \bj_2$ makes with the x-axis of the 2D coordinate system on our shape representation.
We model uncertainty in the approach center as $\by \sim \mN(\hat{\by}, \Sigma_y)$ and uncertainty in the approach angle as $\psi \sim \mN(\hat{\psi}, \sigma_{\psi}^2)$.
For shorthand in the remainder of this paper we will refer to the uncertain approach parameters as $\rho = \{\by, \psi \}$.
In practice $\Sigma_{y}^2$ and $\sigma_{\psi}^2$ can be set from repeatability measurements for a robot~\cite{mooring1986determination}.

@@

\subsection{Grasp Quality}\label{sec:grasp_sample}
We measure the quality of grasp using the probability of force closure~\cite{weisz2012pose, kim2012physically, kehoe2012estimating, kehoe2012toward} given a grasp plan $\Gamma$. Force closure is a binary-valued quantity $F$ that is 1 if the grasp can resist wrenches in arbitrary directions and 0 otherwise.
Let $\mW \in \mathbb{R}^3$ denote the contact wrenches derived from contact locations $\bc_1,\bc_2$, normals $\bn_1,\bn_2$, friction coefficient $\mu$, and center of mass $\bz$ for a given grasp and shape.
If the origin lies within the convex hull of $\mW$, then the grasp is in force closure~\cite{li1988task}.
We rank grasps using the probability of force closure given uncertainty in shape, pose, robot approach, and friction coefficient~\cite{christopoulos2007handling, kehoe2012toward}:

@@

One method to approximately solve Equation~\ref{eq:old_problem_def} is to exhaustively evaluate $P_F(\Gamma_k)$ for all grasp plans in $\mG$ using Monte-Carlo integration and then sort the plans by this quality metric.
We refer to this as a brute force approach. 
This method has been evaluated for shape uncertainty~\cite{christopoulos2007handling, kehoe2012estimating} and pose uncertainty~\cite{weisz2012pose} but may require many samples for each of a large set of candidates to converge to the true value.
More recent work has considered adaptive sampling to discard grasp plans that are not likely to be optimal without fully evaluating their quality~\cite{kehoe2012toward}.

To try and reduce the number of samples needed, we instead maximize the sum of $P_F$ values for each sampled grasp plan $\Gamma_{k,t}$ at time $t$ up to a given time $T_s$:
\begin{align}
    \underset{\Gamma_{k,} \in \mG}{\text{max }} \sum \limits_{t=1}^
    {T_s} P_F \left( \Gamma_{k,t}\right)  \label{eq:problem_def}
\end{align}
\noindent This attempts to perform as well as Equation~\ref{eq:old_problem_def} in as few samples as possible~\cite{srinivas2009gaussian}. We then formulate  problem as a MAB model and compare two different Bayesian MAB algorithms, Thompson Sampling and Gittins Indices.

\section{Grasp Planning as a Multi-Armed Bandit}
We frame the grasp selection problem of \secref{objective} as a MAB problem.
Each arm corresponds to a different grasp plan, $\Gamma_k$, and pulling an arm corresponds to sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the force closure condition. Since force closure is a binary value, each grasp plan $\Gamma_k$ has a Bernoulli reward distribution with probability of force closure, $P_F(\Gamma_k)$.
In a MAB, we want to try and minimize cumulative regret which is an equivalent objective to the objective of Equation~\ref{eq:problem_def}.

@@

\vspace{-2ex}
\begin{align}\label{eq:stopping_condition}
\lbrace t \geq T_s \: \mbox{OR} \: |B(0.025,\alpha_{\bar{k},t},\beta_{\bar{k},t}) -  B(0.975,\alpha_{\bar{k},t},\beta_{\bar{k},t})| \leq \epsilon \rbrace
\end{align}
\noindent where the $\bar{k}$ grasp plan refers to the grasp with the highest estimated $P_F$ at time $t$.

\section{Simulation Experiments}
We used the Brown Vision Lab 2D dataset \cite{brown}, a database of 2D object silhouettes, as in \cite{christopoulos2007handling}.
GPIS models of 3 example objects are visualized using the GPIS-Blur method of~\cite{mahler2015gp} in Figure \ref{fig:shape_samples}.
We downsampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
The measurement noises were assigned uniformly at random to the grid cells.
We then construct a GPIS using the same method proposed in~\cite{mahler2015gp}.
For illustrative purposes, the noise in approach, pose, and friction coefficient were set to the following variances $\sigma_{\psi} = 0.2$ rads, $\sigma_{\by} = 3$ grid cells, $\sigma_{\mu} = 0.4$, $\sigma_{\phi} = 0.3$ rads and $\sigma_{\bt} = 3$ grid cells.
We also performed experiments for the case of two hard contacts in 2-D.
We drew random grasp plans $\Gamma$ by sampling the angle of grasp axis around a circle with radius $\sqrt{2} M$, where $M$ is the dimension of the workspace, and then sampling the circle's origin.

\subsection{Multi-Armed Bandit Experiments}
For our experiments we look at selecting the best grasp out of a size of $|G| = 1000$. We draw samples from our graphical model using the technique described in Sec.  \ref{sec:grasp_sample}. In Fig. \ref{fig:grasp_quality}, we plotted the probability of force closure, $P_F$, of the grasp chosen vs. stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and for the grasps planned by Thompson sampling, Gittins indices, Iterative Pruning \cite{kehoe2012toward} and uniform allocation). Uniform allocation selects a grasp at random from the set to sample next, thus does not use any prior information. Iterative Pruning prunes grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.  We set the discount factor $\gamma =0.98$ for Gittins because that was the highest we could compute the indices for in a feasible amount of time.

>>>>

\title{\LARGE \bf
Multi-Arm Bandit Models for 2D Sample Based Grasp Planning with Uncertainty  [v15 March 15, 2015 ] }

@@

\begin{abstract}
For applications such as warehouse order fulfillment, robot grasps must be robust to uncertainty arising from sensing, shape, mechanics, and control.  One way to achieve this is to evaluate the performance of candidate grasps by sampling perturbations in shape, pose, and control, computing the probability of force closure for each candidate to identify the grasp with the highest expected quality.  This can be computationally demanding and prior work has turned to cloud based computing to solve it. To improve efficiency, we consider how Multi-Armed Bandit (MAB) models for optimizing sequential decisions can be applied in this context. We formulate robust grasp planning as a MAB problem and evaluate grasp planning convergence time using 100 object shapes randomly selected from the Brown Vision 2D Lab Dataset with 1000 uniformly distributed candidate grasp angles. We consider the case where shape uncertainty is represented as a Gaussian process implicit surface (GPIS) and there is Gaussian uncertainty in pose, gripper approach angle, and coefficient of friction.  Non-MAB methods, uniform allocation and iterative pruning, converge slowly.  In contrast, the MAB methods we consider, Thompson Sampling and the Gittins Index, were more efficient in experiments, converging to within 3\% of the optimal grasp approximately 5x faster than non-MAB methods.
\end{abstract}

@@

Consider a robot fulfilling orders in a warehouse, where it encounters new consumer products and must handle them quickly.
Planning grasps using analytic methods requires knowledge of contact locations and surface normals.
However, a robot may not be able to measure these quantities exactly due to sensor imprecision and missing data, which could result from occlusions, transparency, or highly reflective surfaces.

@@

    \caption{Normalized grasp quality over time of the returned grasp for 4 sample-based planning methods.  Normalization divides the current quality of grasp, $P_F(\Gamma_{\bar{k}})$ returned by the highest probability of force closure in the candidate grasp set $P_F(\Gamma^*)$. The highest quality grasp was determined by brute force search over all candidate grasps (which required 10x  more time than any of these methods \cite{kehoe2012toward}).  Data is based on 100 objects randomly selected from from the Brown Vision 2D Lab Dataset \cite{brown} with 1000 uniformly distributed candidate grasp plans. Monte Carlo methods such as Uniform sampling and iterative pruning (eliminating candidates that perform poorly on initial samples) eventually converge to within 3$\%$ of the optimal (the dashed grey line), requiring approximately 40,000 and 20,000 iterations.  Two Multi-Arm Bandit methods perform significantly better, converging after only 4000 iterations.. }%
    \label{fig:grasp_quality}
\end{figure}

One common measure of quality is force closure, the ability to resist external forces and torques in arbitrary directions~\cite{li1988task}. To cope with uncertainty, recent work has explored computing the probability of  force closure given uncertainty in pose~\cite{christopoulos2007handling, kim2012physically, weisz2012pose} and object shape~\cite{kehoe2012estimating, mahler2015gp}.
One way to compute the probability of force closure is using Monte-Carlo integration over sample perturbations in the uncertain quantities\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012toward}. However, performing Monte-Carlo integration for each candidate grasp in a set is computationally expensive.  Past work has looked at using parallel programming in the cloud to overcome this hurdle \cite{kehoe2012estimating,kehoe2012toward,kehoe2015survey} . We show that the Multi-armed Bandit (MAB) model improves upon this brute force approach and could hopefully lead to more efficient cloud based algorithms.

Our main contribution is formulating this problem as  a Multi-Armed Bandit (MAB) and showing it is possible to allocate sampling effort to only grasps that seem promising \cite{barto1998reinforcement, lai1985asymptotically, robbins1985some}. In a standard MAB there are a set of possible options, or `arms'~\cite{barto1998reinforcement}, that each return a numeric reward from a stationary distribution. The goal in a MAB problem is to  select a sequence of options to maximize expected reward. We formulate the problem of ranking a set of candidate grasps according to a quality metric in the presence of uncertainty as a MAB problem. We then treat the MAB algorithm as an anytime algorithm that terminates once a user defined confidence level is met or at a given stopping time.

@@

We compare the performance of Thompson sampling and Gittins indices, two popular algorithms for solving the MAB problem, against uniform allocation and an adaptive sampling method known as iterative pruning, which iteratively reduces the set of candidate grasps  based on sample mean~\cite{kehoe2012toward}. In the task of finding grasps with high probability of force closure.
We compare on the Brown Vision 2D Dataset, a dataset of 2D planar objects~\cite{brown, christopoulos2007handling}.
Our initial results in simulation show that Thompson Sampling, a MAB algorithm, required approximately $5\times$ fewer samples than iterative pruning to plan a grasp within $3\%$ of the estimated highest probability of force closure in the set of 1000 randomly selected grasps averaged over 100 objects.

@@

Some probabilistic grasp quality measures, such as probability of force closure, are computed using Monte-Carlo integration~\cite{christopoulos2007handling, kim2012physically, weisz2012pose, kehoe2012toward}.
Monte-Carlo involves sampling from distributions on uncertainty quantities and averaging the quality over these samples to empirically estimate a probability distribution~\cite{caflisch1998monte}.
However, it can be computationally expensive to sample all proposed grasps to convergence.
To address the computational cost, Kehoe et al.~\cite{kehoe2012estimating} proposed an adaptive sampling procedure called iterative pruning, which periodically discards a subset of the grasps that seem unlikely to be of high probability of force closure. However, the method pruned grasps using only the sample mean, which could discard good grasps.
We propose modeling the problem as a Multi-Armed Bandit, which selects the next grasp to sample based on past observations instead~\cite{barto1998reinforcement, lai1985asymptotically}.

\subsection{MAB Model}
The MAB model, originally described by Robbins \cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision. Solutions to the MAB model have been used in applications for which evaluating all possible options is expensive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.

@@

At each time step the MAB algorithm incurs \textit{regret}, the difference between the expected reward of the best arm and that of the selected arm. Bandit algorithms minimize cumulative regret, the sum of regret over the entire sequence of arm choices.
Lai and Robbins\cite{lai1985asymptotically} showed that the cumulative regret of the optimal solution to the bandit problem is bounded by a logarithmic function of the number of arm pulls.
They presented an algorithm called (Upper Confidence Bound) UCB that obtains this bound asymptotically~\cite{lai1985asymptotically}.
The algorithm maintains a confidence bound on the distribution of reward based on prior observations and pulls the arm with the highest upper confidence bound.
%Many variants of UCB have thus been proposed~\cite{cesa2006prediction}.

@@

\subsubsection{The Gittins Index Method} 
One MAB method is to treat the problem as a Markov Decision Process (MDP) and use Markov Decision theory.
Formally, a MDP is defined as a set of states, a set of actions, a set of transition probabilities between states, a reward function, and a discount factor \cite{barto1998reinforcement}.
In the Beta-Bernoulli MAB case, the set of actions is the $K$ arms and the states are the Beta posterior on each arm, or the integer values of $\alpha_{k,t}$ and $\beta_{k,t}$.

@@

\subsubsection{Thompson Sampling}
Computation of the Gittins indices can increase exponentially in time as the discount factor approaches $1$. The problem with this is that the effective time horizon is a function of $\gamma$. Thus, if the actual horizon is longer than the effective horizon, the method can only pull the current estimate of the best arm \cite{kelly1981multi}. Thus, no longer trading off exploration and exploitation. Thompson sampling is an alternative to the Gittins Index method that isn't prone to such a problem. 
All arms are initialized with prior Beta distributions, which is normally Beta($\alpha_{k,0}=1$,  $\beta_{k,0} =1$) $\forall 1 \leq k \leq K$ to reflect a uniform prior on the parameter of the Bernoulli distribution, $p_{k,0}$.
Then for each arm draw $p_{k,t} \sim \mbox{Beta}(\alpha_{k,t},\beta_{k,t})$ and pull the arm with the highest $p_{k,t}$ drawn.
A reward is then observed, $R_{k,t}$ and the corresponding Beta distribution is updated. The full algorithm is shown in Algorithm 1.

@@

\subsection{Candidate Grasp Model}
The grasp model is illustrated in Fig.~\ref{fig:grasp_model}. We formulate the MAB problem for planar objects using parallel-jaw grippers. Similar to~\cite{mahler2015gp}, we parameterize a grasp using a {\it grasp axis}, the axis of approach for two jaws,  with jaws of width $w_j \in \mathbb{R}$ and a maximum width $w_g \in \mathbb{R}$. The two location of the jaws can be specified as $\mathbf{j}_1,\mathbf{j}_2 \in \mathbb{R}^2$, where $||\mathbf{j}_1 - \mathbf{j}_2|| \leq w_g$. We define a grasp consisting of the tuple $\Gamma = \lbrace \mathbf{j}_1, \mathbf{j}_2 \rbrace$.

%We chose of the line of action model because perturbations to a surface resulting from shape uncertainty lead to changesa in the location of contact with a surface, and the line of action allows us to compute these new locations.

Given a grasp and an object, we define the {\it contact points} as the spatial locations at which the jaws come into contact with the object when following along the grasp axis, $\bc_1, \bc_2 \in \mathbb{R}^2$.
We also refer to the unit outward pointing surface normals at the contact points as $\bn_1, \bn_2 \in \mathbb{R}^2$, the object center of mass as $\bz \in \mathbb{R}^2$ and the friction coefficient as $\mu \in \mathbb{R}$.
%Together these form the set of grasp parameters that allows us to evaluate the forces and torques that a given grasp can apply to an object \cite{ferrari1992}.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width = 6cm, height = 6cm]{figures/Graphical_Model.jpg}
\caption{A graphical model that illustrates the relationship between the different types of uncertainty in an object. As illustrated uncertainty in pose, motion and shape affect the contacts and surface normals that makes up the grasp. Friction coefficient is independent of this relationship.  }
\vspace*{-10pt}
\label{fig:graphical_model}
\end{figure}

@@

Uncertainty in object shape results from sensor imprecision and missing sensor data, which can occur due to transparency, specularity, and occlusions~\cite{mahler2015gp}.
Following ~\cite{mahler2015gp}, we represent the distribution over possible surfaces given sensing noise using a Gaussian process implicit surface (GPIS).
A GPIS represents a distribution over signed distance functions (SDFs).
A SDF is a real-valued function over spatial locations $f: \mathbb{R}^2 \rightarrow \mathbb{R}$ that is greater than 0 outside the object, 0 on the surface and less than 0 inside the object.
A GPIS is a Gaussian distribution over SDF values at a fixed set of query points $\mX = \{\bx_1, ... \bx_n\}, \bx_i \in \mathbb{R}^2$, $f(\bx_i) \sim \mN(\mu_{f}(\bx_i),\Sigma_{f}(\bx_i))$, where $\mu_{f}(\cdot)$ and $\Sigma_{f}(\cdot)$ are the mean and covariance functions of the GPIS~\cite{rasmussen2006}.
See Mahler et al. for details on how to estimate a mean and covariance function and sample shapes from a GPIS~\cite{mahler2015gp}.
For convenience, in later sections we will refer to the GPIS parameters as $\theta = \lbrace \mu_{f}(\bx), \Sigma_{f}(\bx) \rbrace$.

@@

 \subsubsection{Approach Uncertainty}
In practice a robot may not be able to execute a desired grasp $\Gamma = \lbrace \bj_i,\bj_2\rbrace$ exactly due to errors in actuation or feedback measurements used for trajectory following~\cite{kehoe2012estimating}.
We model approach uncertainty as Gaussian uncertainty around the angle of approach and centroid of a straight line grasp $\Gamma$.
Formally, let $\hat{\by} = \frac{1}{2} (\bj_1 + \bj_2)$ denote the center of a planned grasp axis and $\hat{\psi}$ denote the angle that the planned axis $\bj_1 - \bj_2$ makes with the x-axis of the 2D coordinate system on our shape representation.
We model uncertainty in the approach center as $\by \sim \mN(\hat{\by}, \Sigma_y)$ and uncertainty in the approach angle as $\psi \sim \mN(\hat{\psi}, \sigma_{\psi}^2)$.
For shorthand in the remainder of this paper we will refer to the uncertain approach parameters as $\rho = \{\by, \psi \}$.
In practice $\Sigma_{y}^2$ and $\sigma_{\psi}^2$ can be set from repeatability measurements for a robot~\cite{mooring1986determination}.

@@

\subsection{Grasp Quality}\label{sec:grasp_sample}
We measure the quality of grasp using the probability of force closure~\cite{weisz2012pose, kim2012physically, kehoe2012estimating, kehoe2012toward} given a grasp $\Gamma$. Force closure is a binary-valued quantity $F$ that is 1 if the grasp can resist wrenches in arbitrary directions and 0 otherwise.
Let $\mW \in \mathbb{R}^3$ denote the contact wrenches derived from contact locations $\bc_1,\bc_2$, normals $\bn_1,\bn_2$, friction coefficient $\mu$, and center of mass $\bz$ for a given grasp and shape.
If the origin lies within the convex hull of $\mW$, then the grasp is in force closure~\cite{li1988task}.
We rank grasps using the probability of force closure given uncertainty in shape, pose, robot approach, and friction coefficient~\cite{christopoulos2007handling, kehoe2012toward}:

@@

One method to approximately solve Equation~\ref{eq:old_problem_def} is to exhaustively evaluate $P_F(\Gamma_k)$ for all grasp in $\mG$ using Monte-Carlo integration and then sort the plans by this quality metric.
We refer to this as a brute force approach. 
This method has been evaluated for shape uncertainty~\cite{christopoulos2007handling, kehoe2012estimating} and pose uncertainty~\cite{weisz2012pose} but may require many samples for each of a large set of candidates to converge to the true value.
More recent work has considered adaptive sampling to discard grasps that are not likely to be optimal without fully evaluating their quality~\cite{kehoe2012toward}.

To try and reduce the number of samples needed, we instead maximize the sum of $P_F$ values for each sampled grasp  $\Gamma_{k,t}$ at time $t$ up to a given time $T_s$:
\begin{align}
    \underset{\Gamma_{k,} \in \mG}{\text{max }} \sum \limits_{t=1}^
    {T_s} P_F \left( \Gamma_{k,t}\right)  \label{eq:problem_def}
\end{align}
\noindent This attempts to perform as well as Equation~\ref{eq:old_problem_def} in as few samples as possible~\cite{srinivas2009gaussian}. We then formulate  problem as a MAB model and compare two different Bayesian MAB algorithms, Thompson Sampling and Gittins Indices.

\section{Grasp Planning as a Multi-Armed Bandit}
We frame the grasp selection problem of \secref{objective} as a MAB problem.
Each arm corresponds to a different grasp, $\Gamma_k$, and pulling an arm corresponds to sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the force closure condition. Since force closure is a binary value, each grasp $\Gamma_k$ has a Bernoulli reward distribution with probability of force closure, $P_F(\Gamma_k)$.
In a MAB, we want to try and minimize cumulative regret which is an equivalent objective to the objective of Equation~\ref{eq:problem_def}.

@@

\vspace{-2ex}
\begin{align}\label{eq:stopping_condition}
\lbrace t \geq T_s \: \mbox{OR} \: |B(0.025,\alpha_{\bar{k},t},\beta_{\bar{k},t}) -  B(0.975,\alpha_{\bar{k},t},\beta_{\bar{k},t})| \leq \epsilon \rbrace
\end{align}
\noindent where the $\bar{k}$ grasp refers to the grasp with the highest estimated $P_F$ at time $t$.

\section{Simulation Experiments}
We used the Brown Vision Lab 2D dataset \cite{brown}, a database of 2D planar objects, as in \cite{christopoulos2007handling}.
GPIS models of 3 example objects are visualized using the GPIS-Blur method of~\cite{mahler2015gp} in Figure \ref{fig:shape_samples}.
We downsampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values.
The measurement noise were assigned uniformly at random to the grid cells.
We then construct a GPIS using the same method proposed in~\cite{mahler2015gp}.
For illustrative purposes, the noise in approach, pose, and friction coefficient were set to the following variances $\sigma_{\psi} = 0.2$ rads, $\sigma_{\by} = 3$ grid cells, $\sigma_{\mu} = 0.4$, $\sigma_{\phi} = 0.3$ rads and $\sigma_{\bt} = 3$ grid cells.
We also performed experiments for the case of two hard contacts in 2-D.
We drew random grasps $\Gamma$ by sampling the angle of grasp axis around a circle with radius $\sqrt{2} M$, where $M$ is the dimension of the workspace, and then sampling the circle's origin. All experiments were run on machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB 1600 MHz memory in Matlab 2014a.

\subsection{Multi-Armed Bandit Experiments}
For our experiments we look at selecting the best grasp out of a size of $|G| = 1000$. We draw samples from our graphical model using the technique described in Sec.  \ref{sec:grasp_sample}. In Fig. \ref{fig:grasp_quality}, we plotted the probability of force closure, $P_F$, of the grasp chosen vs. stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and for the grasps planned by Thompson sampling, Gittins indices, iterative pruning \cite{kehoe2012toward} and uniform allocation). Uniform allocation selects a grasp at random from the set to sample next, thus does not use any prior information. iterative pruning prunes grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.  We set the discount factor $\gamma =0.98$ for Gittins because that was the highest we could compute the indices for in a feasible amount of time.
